A sheaf--function dictionary for algebraic tori over local fields

### 2013-08-19 shanghai.tex
Citation added.

In Part 1 of this paper we study the category $\QC(G)$ of quasicharacter sheaves.
Since it is a rigid symmetric monoidal category
the set of isomorphism classes $\QCiso{G}$ forms a group.
Motivated by the sheaf--function dictionary for commutative, connected
algebraic groups \cite{deligne:SGA4.5},\David{more specific citation} we explore the trace of Frobenius morphism
\[
\QCiso{G} \to \Hom(G(\Fq), \EEx)
\]
and show that it is an isomorphism in Theorem~\ref{thm:snake}, assuming only
that the geometric component group of $G$ is finitely generated.

>>>>

In Part 1 of this paper we study the category $\QC(G)$ of quasicharacter sheaves.
Since it is a rigid symmetric monoidal category
the set of isomorphism classes $\QCiso{G}$ forms a group.
Motivated by the sheaf--function dictionary for commutative, connected
algebraic groups \cite{deligne:SGA4.5}*{sommes trig.}, 
we explore the trace of Frobenius morphism
\[
\QCiso{G} \to \Hom(G(\Fq), \EEx)
\]
and show that it is an isomorphism in Theorem~\ref{thm:snake}, assuming only
that the geometric component group of $G$ is finitely generated.
